### 2022-03-09 src/text/3-applications.tex
reorder subsection

Gammapy can be used for a variety of science cases by different IACT experiments.
In this section, we show a non-exhaustive list of some typical analysis that be performed.

@@

\subsection{A 3D likelihood analysis}
\label{ssec:1D-analysis}
\input{3-applications-subsections/3.2-3D-analysis}
\todo{Laura}

@@

\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
Ref:~\citep{Stewart2009}

>>>>

Gammapy can be used for a variety of science cases by different IACT experiments. (Refer to publications)
In this section, we show a non-exhaustive list of some typical analysis that be performed.

@@

\subsection{A 3D likelihood analysis}
\label{ssec:3D-analysis}
\input{3-applications-subsections/3.2-3D-analysis}
\todo{Laura}

@@

\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
Ref:~\citep{Stewart2009}
\begin{figure*}[t]
        \centering
        \includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
        \caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
\end{figure*}
